---
title: "Binomial, Negative Binomial Practice Problems"
format: 
  html:
    self-contained: true
editor_options: 
  chunk_output_type: console
knitr: 
  opts_chunk: 
    dev: svg
---

1. The probability of completing a difficult PhD program is 0.7.  Calculate the probability that in a cohort of 29 students, 3 or fewer students do not complete the degree.
[3 of 29] -> Binomial 
x ~ binomial (N= 29, p= 0.7, p -> in terms of completing 
P(X = 29,28,27,26) or P(X>=26) =
pbinom(in R) 1-P(X<26), Pbinom(
```{r}
1- pbinom(25, 28, 0.7)
sum(dbinom(26:29, 29, 0.7))
pbinom(3,29,0.3)
```

1. In this difficult program, students complete the degree after 5 years (no variation).  A professor decides to stop taking new students after advising 10 students to completion.  She also decides to retire after all of her active students graduate.  If the professor only takes 1 student a year (at the start of the program), what is the probability that the professor will be retired in 20 years?

```{r}

```


1. 3 prizes are awarded to the first 3 correct solutions of a difficult problem.  Suppose the probability of a correct solution is 0.1.  What is the probability that all three prizes will be awarded by the 25th submission?
W~ NegBinomial(k = 3, p = 0.1)
```{r}
pnbinom(22, 3, 0.1)
```








